### 2019-05-30 doc/appendix/appendixexemple.tex
added some labels

\chapter{Arbitrary Appendix}
\label{chap:appendix_arb}
\endgroup

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc, Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realizes why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is more simple and regular than that of the individual languages. The new common language will be more simple and regular than the existing European languages. It will be as simple as Occidental; in fact, it will be Occidental.

>>>>

\chapter{Practical Challenges with Stainless}
\label{chap:appendix_arb}
\endgroup

\section{Integration}

During this work, Stainless bumped the sbt plugin from version 0.13.17 to 1.2.8 and Scala from 2.11.12 to 2.12.8.
So this section might be out of date now.

Bitcoin-S-Core uses sbt 1.2.8 and Scala 2.12.8, while Stainless sbt plugin is on sbt 0.13.17 and Scala 2.11.12.

Sbt introduced new features in the 1.x release used by Bitcoin-S.
Most of them can be written the sbt 0.13.17 way.

The bigger problem is, due to the different Scala and sbt versions, the error message, after trying to go in a sbt shell.
\begin{verbatim}
  [warn] There may be incompatibilities among your library dependencies; run 'evicted'
         to see detailed eviction warnings.
  [error] java.lang.NoClassDefFoundError: sbt/SourcePosition
  ...
  Project loading failed: (r)etry, (q)uit, (l)ast, or (i)gnore?
\end{verbatim}

Downgrading Bitcoin-S sbt version to 0.13.17 fixes the error but then it can not load some libraries only compiled for newer versions.
So this would take too much time to fix and changes the Bitcoin-S code unwantingly.

The next approach is to use stainless cli instead of sbt.
Running stainless on all source files does not work, because the dependencies are missing.
The parameter \emph{-classpath} can resolve it but the value of this parameter must be the paths to all the dependencies separated by a ':'.
Finally, \emph{core} depends on \emph{secp256k1jni}, another package of Bitcoin-S written in Java.
So this needs to be in the source files to.

The final command looks like this in \emph{core} folder of Bitcoin-S:
\begin{lstlisting}[language=bash]
  $ stainless
    -classpath ".:$(find ~/.ivy2/ -type f -name *.jar | tr '\n' ':')"
    $(find . -type f -name *.scala | tr '\n' ' ')
    $(find ../secp256k1jni -type f -name *.java | tr '\n' ' ')
\end{lstlisting}

The output was some Stainless error.
\begin{verbatim}
  [Internal] Error: object scala.reflect.macros.internal.macroImpl in compiler mirror
             not found.. Trace:
  [Internal] - scala.reflect.internal.MissingRequirementError$.signal
             (MissingRequirementError.scala:17)
  ...
  [Internal] object scala.reflect.macros.internal.macroImpl in compiler mirror not found.
  [Internal] Please inform the authors of Inox about this message
\end{verbatim}

After some discussion, we decided to go another way, because the errors may take too much time and it might lead to a next error.
Let's extract the code needed to verify a transaction mainly the class Transaction and ScriptInterpreter with many other classes their depending on.

After this extraction Stainless was successfully integrated with both, sbt and JAR.
This leads us to another finding as described in the next section.

\section{Error Reporting with sbt and JAR}

Running \code{sbt compile} in the project with Stainless ended without error.
But it also ended with no output.
So we were not able to change the code so Stainless would accept it.

After running the JAR file on the code there were many errors as described in chapter \ref{chap:verify_add}.

So the sbt plugin does not complain always but the JAR file did.
The open issue \mypound484 on GitHub might describe this error.

### 2019-05-30 doc/chapters/towards_verifying_addition.tex
added section result
added some labels

\chapter{Towards Verifying Addition with Zero}
After realizing, that it would consume to much time to rewrite the Bitcoin-S code and even the extracted part with checkTransaction, we decided to extract the smallest unit in Bitcoin-S-Core that is worthwhile to verify.
We found the addition of two Satoshis would be a good candidate.
To make it even easier, we decided to verify only the addition of some satoshis with zero.

@@

>>>>

\chapter{Towards Verifying Addition with Zero}
\label{chap:verify_add}

After realizing, that it would consume to much time to rewrite the Bitcoin-S code and even the extracted part with checkTransaction, we decided to extract the smallest unit in Bitcoin-S-Core that is worthwhile to verify.
We found the addition of two Satoshis would be a good candidate.
To make it even easier, we decided to verify only the addition of some satoshis with zero.

@@

\section{Result}
